Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments

### 2021-06-28 doc/paper.Rmd
add conflict of interest statement
higher resolution high-res figures

We thank Collin Edwards, \_\_\_, \_\_\_, and \_\_\_ anonymous reviewers for helpful discussions and comments on the manuscript.
We also thank the technicians and students who helped conduct the *Heliconia* censuses and the BDFFP and INPA for logistical support.
Financial support was provided by the U.S.
National Science Foundation (awards DEB-0614339, DEB-0614149, INT 98-06351, and DEB-1948607).
This is publication No. \_\_\_ in the BDFFP Technical Series.

@@

```{r eda_hires, fig.height=7, fig.width=7, dev='tiff', include=FALSE}
tar_read(eda_plot) & theme(text = element_text(size = 10))
```

@@

```{r surv-curve_hires, fig.height=3.5, fig.width=7, dev="tiff", include=FALSE}
tar_read(surv_curve) + theme(text = element_text(size = 10))
```

@@

```{r size-plot_hires, fig.width=7, fig.height=7, dev='tiff', include=FALSE}
tar_read(size_plot) & theme(text = element_text(size = 10))
```

@@

```{r surv-spei_hires, fig.height=7.5, fig.width=7, dev='tiff', include=FALSE}
tar_read(s_spei_plot) & theme(text = element_text(size = 10))
```

@@

```{r growth-spei_hires, fig.height=7.5, fig.width=7, dev='tiff', include=FALSE}
tar_read(g_spei_plot) & theme(text = element_text(size = 10))
```

@@

```{r flwr-spei_hires, fig.height=7.5, fig.width=7, dev='tiff', include=FALSE}
tar_read(f_spei_plot) & theme(text = element_text(size = 10))
```

>>>>

We thank Collin Edwards, \_\_\_, \_\_\_, and \_\_\_ anonymous reviewers for helpful discussions and comments on the manuscript.
We also thank the technicians and students who helped conduct the *Heliconia* censuses and the BDFFP and INPA for logistical support.
Financial support was provided by the U.S.
National Science Foundation (awards DEB-0614339, DEB-0614149, INT 98-06351, and DEB-1948607).
This is publication No. \_\_\_ in the BDFFP Technical Series.
The authors delcare no conflicts of interest.

@@

```{r eda_hires, fig.height=7, fig.width=7, dev='tiff', include=FALSE, dpi=600}
tar_read(eda_plot) & theme(text = element_text(size = 10))
```

@@

```{r surv-curve_hires, fig.height=3.5, fig.width=7, dev="tiff", dpi=600, include=FALSE}
tar_read(surv_curve) + theme(text = element_text(size = 10))
```

@@

```{r size-plot_hires, fig.width=7, fig.height=7, dev='tiff', dpi=600, include=FALSE}
tar_read(size_plot) & theme(text = element_text(size = 10))
```

@@

```{r surv-spei_hires, fig.height=7.5, fig.width=7, dev='tiff', dpi=600, include=FALSE}
tar_read(s_spei_plot) & theme(text = element_text(size = 10))
```

@@

```{r growth-spei_hires, fig.height=7.5, fig.width=7, dev='tiff', dpi=600, include=FALSE}
tar_read(g_spei_plot) & theme(text = element_text(size = 10))
```

@@

```{r flwr-spei_hires, fig.height=7.5, fig.width=7, dev='tiff', dpi=600, include=FALSE}
tar_read(f_spei_plot) & theme(text = element_text(size = 10))
```
